---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
  html_document:
    self_contained: false
    toc: true
    toc_float: false
---

```{r rsetup,eval=TRUE,include=FALSE}
require(codecheck)
require(knitr)
require(rprojroot)
require(yaml)
require(xtable)
require(tibble)
require(readr)
options(width=60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path=FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```


# Summary

This code was straightforward to check. All original code was provided and took minimal computation time to run. The figures were reproduced with the correct features and formatted as in the ReScience paper.

\clearpage

# CODECHECKER notes

The original code was provided in the GitHub repo here: https://github.com/ReScience-Archives/Detorakis-2017/tree/master/code.
Code was written in Python 3.6.1 and the README gave explanations for all scripts. 
To run the code I first cloned the repo in a Linux terminal. I then created a conda environment called detorakis_1 in the cloned repo and installed the package versions given in the README:

```
$ conda create -n detorakis_1 python=3.6
$ conda activate detorakis_1
$ conda install numpy==1.13.1
$ conda install scipy==0.19.1
$ conda install matplotlib==2.0.2
```

I then ran the code using:

```
$ python run_all.py
```

The figures were produced within 15 seconds. Figures 2 and 3 were reproduced and plotted in the format given in the ReScience paper. Figure 1 was initially plotted as very squashed compared to the ReScience paper. However when I pressed the minimize button twice the image formatted itself correctly and I could save all three figures into the figures folder.

\setcounter{table}{0}
\setcounter{figure}{0}
\captionsetup[table]{labelformat=addC}
\captionsetup[figure]{labelformat=addC}

\clearpage

```{r, echo=FALSE, fig.cap=manifest_df[1:3,"comment"]}
# TODO turn into a loop 
knitr::include_graphics(manifest_df[1, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[2, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[3, "dest"])
cat('\n\n')
```

\clearpage



## Acknowledgements

CODECHECK is financially supported by the Mozilla foundation.



<!-- Do not edit below -->

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
